Calculate FD

### 2020-07-24 analysis/calc_fd.Rmd

  future::plan(multiprocess)
  fd <- future_map(group_plots$plot_id, get_fd_safe, data = group_data) %>%
    rbind()

@@

fd <- map(1:num_groups, get_parallel_FD, data = data)
```

@@

library(furrr)
future::plan(multiprocess)
system.time(fd <- future_map(plots_left, get_fd_safe, data = data))
```

>>>>

  future::plan(multiprocess)
  fd <- future_map(group_plots$plot_id, get_fd_safe, obs_data = group_data) %>%
    rbind()

@@

fd <- map(1:num_groups, get_parallel_FD, obs_data = data)
```

@@

library(furrr)
future::plan(multiprocess)
system.time(fd <- future_map(plots_left, get_fd_safe, obs_data = data))
```
